State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-02-09 draft.tex
no idea
corrected cor15
Corrected corollary 15, removed some tickets and changed the bounds on
M in (3.19) and (3.20)

%% Ticketing System
\usepackage{etoolbox}
\usepackage{xparse}
\NewDocumentCommand{\openTickets}{ > {\SplitList {,} } m }{\ProcessList{#1}{\BoolInit}}
\newcommand{\BoolInit}[1]{\providetoggle{#1}\toggletrue{#1}}
\newcommand{\todo}[2]{%
  \providetoggle{#1}%
    \iftoggle{#1}{%
    {\color{red}#2}%
    }{#2}
}

%% Ticket list
\openTickets{Manuel:wlog,Manuel:convHull,Manuel:remConcavity,Manuel:thm14:ref,Manuel:invertability:assumption,Manuel:inclusion:step,Manuel:minus:one,Manuel:proof:thm14}

@@

\emph{Notation:} Throughout this paper 
%
we denote sequences of integers $\mathbb N_m = \{1,\ldots,m\}$ for $m\geq 1$ and $\mathbb N_{[n,m]} = \{n,\ldots,m\}$ for $n\leq m$.
%
Given a collection of row-vectors $a_i$ and scalars $b_i$ for $i\in\mathbb N_m$, we denote as ${\bf{a}}_{\mathcal I}$ and ${\bf{b}}_{\mathcal I}$ the matrix and vector, respectively, with rows $a_i$ and $b_i$ for all indices $i$ in the index set $\mathcal I\subseteq \mathbb N_m$.
%
We denote the image of a set $\mathcal C\subseteq X$ under the map $f:X\mapsto Y$ as $f\vert_{\mathcal C} = \{y\in Y:\exists x\in\mathcal C,\;y=f(x)\}$, and for $f(x) = Ax$ we write $f\vert_{\mathcal{C}} = A\mathcal{C}$.
%
For $x\in\mathbb R^n$ the Euclidean norm is denoted $\|x\|=\sqrt{x^T x}$, and we define the weighted norm $\|x\|_P=\sqrt{x^T P x}$ for a positive definite matrix $P\in\mathbb R^{n\times n}$, and for any $\epsilon > 0$ we define the ball $B_\epsilon(x) = \{y\in\mathbb R^n : \|x-y\| \leq \epsilon\}$.

@@

\begin{rem}\label{rem:pPdiff:calculation}
For a convex polyhedron $S=\{x : h_i x \leq 1$ $\forall i \in\mathcal{I} \}$ the parametric Pontryagin difference $S \ominus \mathcal{V}(S)$ is given by
%
%The parametric Pontryagin difference $S \ominus \mathcal{V}(S)$, for a convex polyhedral set $S=\{x : h_i x \leq 1\ \forall i \in\mathcal{I} \}$, is given by
%
%and a para\-met\-rically convex polytopic set $\mathcal{V}(x)$, we have 
% \begin{align*}
% S \ominus \mathcal{V}(S) 
% &= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
% \ \forall i \in\mathcal{I} \}\\
% &= \{x : h_i x + \max_{j} h_i v_j(x) \leq 1 
% \ \forall i \in\mathcal{I}\}\\
% &= \{x : h_i x + \zeta_i(x) \leq 1 
% \ \forall i \in\mathcal{I}\}, \ 
% \zeta_i(x) = \max_{j} h_i v_j(x)
% \end{align*}
\begin{align*}
S \ominus \mathcal{V}(S) 
&= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
\ \forall i \in\mathcal{I} \}\\
&= \{x : h_i x + \underbrace{\max_{j} h_i v_j(x)}_{=\zeta_i(x)} \leq 1 
\ \forall i \in\mathcal{I}\} .
\end{align*}
Here $\zeta_i(x)$ is the solution of a mpLP and hence is a continuous \todo{Manuel:remConcavity}{and concave} piecewise affine function of $x$~\cite{Gal:1995}. It follows that $S\ominus\mathcal{V}(S)$ is a convex polyhedral set.
%
To compute $\zeta_i(x)$ for all $x\in\mathcal X$ is in general a challenging problem, and a simpler method of determining the supporting hyperplanes of $S\ominus\mathcal{V}(S)$ is to include all possible affine inequalities in the set description:
\[
S\ominus\mathcal{V}(S) = \{ x : h_ix + h_i v_j(x) \leq 1, \ \forall j\in\mathbb{N}_q\ \forall i\in \mathcal I\}
\] 
and to subsequently remove redundant inequalities by applying an inequality reduction algorithm. 
% \textcolor{red}{%
The resulting set can be expressed $S\ominus \mathcal{V}(S) = \{ x : h_i^\prime x \leq 1 \ \forall i \in \mathcal{I}^\prime \}$.%
% }%
\end{rem}
%

@@

%We next provide conditions under which Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
% whenever the MRPI set $\mathcal X^\infty$ is non-empty. 
%
We next show that Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations if:
%
(i) $\Psi$ is asymptotically stable, and 
%
(ii) $\Gamma$ exists such that $(\Psi,\Gamma)$ is an observable pair and $\Gamma x$ is finite whenever $x\in\mathcal{X}$.
%
%We next show that, under mild conditions, Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
%
%, so that the spectral radius, $\rho$, of $\Psi$ satisfies $\rho < 1$. We denote the pre-image of a set $S$ under the linear map $\Psi$ as $\Psi^{-1}S$; 
%
The finite determinability of the MRPI set
$\mathcal X^\infty$ implies that there exists a finite number, $M$, such 
that $\mathcal X^\infty = \mathcal X_M$, and hence  $\mathcal{X}^\infty$ is defined by a finite set of linear inequalities whenever $\mathcal X^\infty\neq \emptyset$.
%
%that $x\in\mathcal X_M$ implies $\Psi x + v \in\mathcal X_M$ for all $v\in\mathcal V(x)$, and hence $\mathcal X^\infty = \mathcal X_M$.
%
\begin{thm}\label{thm:finite:MRPI:set:state:dependable}
Let $\rho < 1$, where $\rho$ is the spectral radius of $\Psi$, and let $\mathcal{X}\subseteq\mathcal{P}$, $\mathcal{P}=\{x:\Gamma x\leq{\bf{1}}\wedge 
-\Gamma x\leq{\bf{1}}\}$, where $(\Psi,\Gamma)$ is an observable pair.
%
Then the MRPI set $\mathcal X^\infty$ for the system $x^+ = \Psi x + v$ subject to disturbances $v\in\mathcal{V}(x)$, where $\mathcal V(x)$ is a continuous \todo{Manuel:thm14:ref}{and piece-wise affine point-to-set map as defined in~\eqref{eq:definition:PWA:polytopic:set:cl}}, and constraints $x\in\mathcal{X}$, is either empty or else is a bounded polytopic set satisfying $\mathcal X^\infty =\mathcal X_M$ for finite $M$.
\end{thm}
%
%
\begin{proof}
From~\eqref{eq:Xk:iteration} and Proposition~\ref{prop:Dk:iteration} it is clear that $\mathcal X^\infty$ is empty if $\mathcal{R}_k =\emptyset$ for some $k\geq 0$.
%
For the remainder of the proof we assume that $\mathcal{R}^\infty \neq \emptyset$ exists such that $\mathcal{R}_k \supseteq \mathcal{R}^\infty$ for all $k$.
%
The proof has two main steps: 
%
(i) we prove boundedness of $\mathcal X_k$ for all $k\geq n$, where $n$ is the state dimension;
%
(ii) we show that $\mathcal D_k$ grows exponentially with $k$, so that, for any bounded set $\mathcal C$, finite $M$ exists such that $\mathcal D_{M+1}\supseteq \mathcal{C}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_{M}$ and deducing that $\mathcal X^\infty = \mathcal X_M$. 
%

@@

To see that $\mathcal{D}_k$ grows exponentially, let $r_1$ be the radius of the largest ball centred on the origin that is contained in $\mathcal{R}^\infty$ so that $\mathcal{R}^\infty \supseteq r_1\mathcal{E}$ (where 
for notational convenience we write $\mathcal E=B_1(0)$). Then Proposition~\ref{prop:Dk:iteration} implies $\mathcal{D}_k=\Psi^{-k}\mathcal{R}_k\supseteq\todo{Manuel:inclusion:step}{\Psi^{-k}\mathcal R^\infty\supseteq}\rho^{-k}r_1\mathcal{E}$.

@@

To complete the proof, let $r_2$ denote the radius of the smallest ball centred on the origin that contains $\mathcal X_n$.
%(noting that $\mathcal X_p$ is necessarily bounded for $p\geq n$). 
%
Then, for any $k\geq n+1$ such that 
$\rho^{-k} r_1 \geq r_2$, 
we can conclude that $D_k\supseteq \mathcal X_n$ and, since $\mathcal X_n \supseteq \mathcal X_{k-1}$, we also have $D_k\supseteq \mathcal X_{k-1}$ so that 
$\mathcal X_k \todo{Manuel:proof:thm14}{\supseteq} \mathcal{X}_{k-1} \cap D_k$.
%
Therefore $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:bound}
M = \max \left\{ n , \left\lceil \frac{\log(r_2/r_1)}{\log(1/\rho)}\right\rceil \todo{Manuel:minus:one}{- 1} \right\},
\end{equation}
and it follows that $\mathcal{X}^\infty$ is a bounded polytopic set.
\end{proof}
%

@@

\begin{cor}
Let $c_1$, $c_2$ and $c_3$ denote respectively the radii of: %
the largest ball centered on the origin contained in $\mathcal{X}$, 
%
the smallest ball centered on the origin that contains $\mathcal{P}_n$, and
%
the smallest ball centered on the origin that contains $\mathcal{V}(x)$ for all $x\in\mathcal{X}$.
%
If $c_1\geq (1-\rho)^{-1}c_3$, then $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:cbound}
M = \max \left\{ n , \left\lceil \frac{1}{\log(1/\rho)}\log\left(\frac{c_2-(1-\rho)^{-1}c_3}{c_1-(1-\rho)^{-1}c_3}\right)\right\rceil - 1 \right\}.
\end{equation}
\end{cor}
%

\begin{proof}
If $\mathcal{V}(x)\subseteq c_3\mathcal{E}$ for all $x\in\mathcal{X}$, then since $\mathcal{X}_k\subseteq\mathcal{X}$ for all $k$, we have $\mathcal{R}_k \supseteq \mathcal{R}_{k-1}\ominus \rho^{k-1} c_3\mathcal{E}$ from (\ref{eq:Rk:iteration}), and hence
\[
\mathcal{R}_k \supseteq \mathcal{X} \ominus \sum_{i=0}^{k-1} \rho^{i} c_3\mathcal{E} 
%=\mathcal{X} \ominus \Bigl(\frac{1-\rho^k}{1-\rho} \Bigr) c_3 \mathcal{E}.
\supseteq \Bigl[ c_1 - \Bigl(\frac{1-\rho^k}{1-\rho} \Bigr) c_3\Bigr] \mathcal{E}.
\]
where $c_1 \mathcal{E} \subseteq \mathcal{X}$. 
%
Therefore $\mathcal{R}^\infty \supseteq \bigl( c_1 - (1-\rho)^{-1}c_3\bigr) \mathcal{E} \neq \emptyset$ if $c_1\geq (1-\rho)^{-1}c_3$,
%
in which case $\mathcal{X}_k \subseteq \mathcal{P}_n \subseteq c_2 \mathcal{E}$ for all $k\geq n$ implies that $\mathcal X^\infty = \mathcal X_M$ where $M$ is given by (\ref{eq:iteration:cbound}).
\end{proof}

>>>>

%% Ticketing System
\usepackage{etoolbox}
\usepackage{xparse}
\NewDocumentCommand{\openTickets}{ > {\SplitList {,} } m }{\ProcessList{#1}{\BoolInit}}
\newcommand{\BoolInit}[1]{\providetoggle{#1}\toggletrue{#1}}
\newcommand{\todo}[2]{%
  \providetoggle{#1}%
    \iftoggle{#1}{%
    {\color{red}#2}%
    }{#2}%
}

%% Ticket list
\openTickets{Manuel:wlog,Manuel:invertability:assumption,Mark:log:bounds,Mark:proof:cor15}

@@

\emph{Notation:} Throughout this paper 
%
we denote sequences of integers $\mathbb N_m = \{1,\ldots,m\}$ for $m\geq 1$ and $\mathbb N_{[n,m]} = \{n,\ldots,m\}$ for $n\leq m$.
%
Given a collection of row-vectors $a_i$ and scalars $b_i$ for $i\in\mathbb N_m$, we denote as ${\bf{a}}_{\mathcal I}$ and ${\bf{b}}_{\mathcal I}$ the matrix and vector, respectively, with rows $a_i$ and $b_i$ for all indices $i$ in the index set $\mathcal I\subseteq \mathbb N_m$.
%
For $x\in\mathbb R^n$ the Euclidean norm is denoted $\|x\|=\sqrt{x^T x}$, and we define the weighted norm $\|x\|_P=\sqrt{x^T P x}$ for a positive definite matrix $P\in\mathbb R^{n\times n}$, and for any $\epsilon > 0$ we define the ball $B_\epsilon(x) = \{y\in\mathbb R^n : \|x-y\| \leq \epsilon\}$.
%
We denote the image of a set $\mathcal C\subseteq X$ under the map $f:X\mapsto Y$ as $f\vert_{\mathcal C} = \{y\in Y:\exists x\in\mathcal C,\;y=f(x)\}$, and for $f(x) = Ax$ we write $f\vert_{\mathcal{C}} = A\mathcal{C}$.
%
The Minkowski sum, $\mathcal{X}\oplus\mathcal{Y}$, of sets $\mathcal{X},\mathcal{Y}\subseteq\mathbb{R}^n$ is the set $\{z: \exists x\in\mathcal{X}, y\in\mathcal{Y} : z = x+y\}$.
%

@@

\begin{rem}\label{rem:pPdiff:calculation}
For a convex polyhedron $S=\{x : h_i x \leq 1$ $\forall i \in\mathcal{I} \}$ the parametric Pontryagin difference $S \ominus \mathcal{V}(S)$ is given by
%
%The parametric Pontryagin difference $S \ominus \mathcal{V}(S)$, for a convex polyhedral set $S=\{x : h_i x \leq 1\ \forall i \in\mathcal{I} \}$, is given by
%
%and a para\-met\-rically convex polytopic set $\mathcal{V}(x)$, we have 
% \begin{align*}
% S \ominus \mathcal{V}(S) 
% &= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
% \ \forall i \in\mathcal{I} \}\\
% &= \{x : h_i x + \max_{j} h_i v_j(x) \leq 1 
% \ \forall i \in\mathcal{I}\}\\
% &= \{x : h_i x + \zeta_i(x) \leq 1 
% \ \forall i \in\mathcal{I}\}, \ 
% \zeta_i(x) = \max_{j} h_i v_j(x)
% \end{align*}
\begin{align*}
S \ominus \mathcal{V}(S) 
&= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
\ \forall i \in\mathcal{I} \}\\
&= \{x : h_i x + \underbrace{\max_{j} h_i v_j(x)}_{=\zeta_i(x)} \leq 1 
\ \forall i \in\mathcal{I}\} .
\end{align*}
Here $\zeta_i(x)$ is the solution of a mpLP and hence is a continuous and concave piecewise affine function of $x$~\cite{Gal:1995}. It follows that $S\ominus\mathcal{V}(S)$ is a convex polyhedral set.
%
To compute $\zeta_i(x)$ for all $x\in\mathcal X$ is in general a challenging problem, and a simpler method of determining the supporting hyperplanes of $S\ominus\mathcal{V}(S)$ is to include all possible affine inequalities in the set description:
\[
S\ominus\mathcal{V}(S) = \{ x : h_ix + h_i v_j(x) \leq 1, \ \forall j\in\mathbb{N}_q\ \forall i\in \mathcal I\}
\] 
and to subsequently remove redundant inequalities by applying an inequality reduction algorithm. 
% \textcolor{red}{%
The resulting set can be expressed $S\ominus \mathcal{V}(S) = \{ x : h_i^\prime x \leq 1 \ \forall i \in \mathcal{I}^\prime \}$.%
% }%
\end{rem}
%

@@

%We next provide conditions under which Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
% whenever the MRPI set $\mathcal X^\infty$ is non-empty. 
%
We next show that Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations if:
%
(i) $\Psi$ is asymptotically stable, and 
%
(ii) $\Gamma$ exists such that $(\Psi,\Gamma)$ is an observable pair and $\Gamma x$ is finite whenever $x\in\mathcal{X}$.
%
%We next show that, under mild conditions, Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
%
%, so that the spectral radius, $\rho$, of $\Psi$ satisfies $\rho < 1$. We denote the pre-image of a set $S$ under the linear map $\Psi$ as $\Psi^{-1}S$; 
%
The finite determinability of the MRPI set
$\mathcal X^\infty$ implies that there exists a finite number, $M$, such 
that $\mathcal X^\infty = \mathcal X_M$, and hence  $\mathcal{X}^\infty$ is defined by a finite set of linear inequalities whenever $\mathcal X^\infty\neq \emptyset$.
%
%that $x\in\mathcal X_M$ implies $\Psi x + v \in\mathcal X_M$ for all $v\in\mathcal V(x)$, and hence $\mathcal X^\infty = \mathcal X_M$.
%
\begin{thm}\label{thm:finite:MRPI:set:state:dependable}
Let $\rho < 1$, where $\rho$ is the spectral radius of $\Psi$, and let $\mathcal{X}\subseteq\mathcal{P}$, $\mathcal{P}=\{x:\Gamma x\leq{\bf{1}}\wedge 
-\Gamma x\leq{\bf{1}}\}$, where $(\Psi,\Gamma)$ is an observable pair.
%
Then the MRPI set $\mathcal X^\infty$ for the system $x^+ = \Psi x + v$ subject to disturbances $v\in\mathcal{V}(x)$, where $\mathcal V(x)$ is a continuous and piece-wise affine point-to-set map as defined in~\eqref{eq:definition:PWA:polytopic:set:cl}, and constraints $x\in\mathcal{X}$, is either empty or else is a bounded polytopic set satisfying $\mathcal X^\infty =\mathcal X_M$ for finite $M$.
\end{thm}
%
%
\begin{proof}
From~\eqref{eq:Xk:iteration} and Proposition~\ref{prop:Dk:iteration} it is clear that $\mathcal X^\infty$ is empty if $\mathcal{R}_k =\emptyset$ for some $k\geq 0$.
%
For the remainder of the proof we assume that $\mathcal{R}^\infty \neq \emptyset$ exists such that $\mathcal{R}_k \supseteq \mathcal{R}^\infty$ for all $k$.
%
The proof has two main steps: 
%
(i) we prove boundedness of $\mathcal X_k$ for all $k\geq n$, where $n$ is the state dimension;
%
(ii) we show that $\mathcal D_k$ grows exponentially with $k$, so that, for any bounded set $\mathcal C$, finite $M$ exists such that $\mathcal D_{M+1}\supseteq \mathcal{C}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_{M}$ and deducing that $\mathcal X^\infty = \mathcal X_M$. 
%

@@

To see that $\mathcal{D}_k$ grows exponentially, let $r_1$ be the radius of the largest ball centred on the origin that is contained in $\mathcal{R}^\infty$ so that $\mathcal{R}^\infty \supseteq r_1\mathcal{E}$ (where 
for notational convenience we write $\mathcal E=B_1(0)$). Then Proposition~\ref{prop:Dk:iteration} implies $\mathcal{D}_k=\Psi^{-k}\mathcal{R}_k\supseteq\Psi^{-k}\mathcal R^\infty\supseteq \rho^{-k}r_1\mathcal{E}$.

@@

To complete the proof, let $r_2$ denote the radius of the smallest ball centred on the origin that contains $\mathcal X_n$.
%(noting that $\mathcal X_p$ is necessarily bounded for $p\geq n$). 
%
Then, for any $k\geq n+1$ such that 
$\rho^{-k} r_1 \geq r_2$, 
we can conclude that $D_k\supseteq \mathcal X_n$ and, since $\mathcal X_n \supseteq \mathcal X_{k-1}$, we also have $D_k\supseteq \mathcal X_{k-1}$ so that 
$\mathcal X_k = \mathcal{X}_{k-1}$.
%
Therefore $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:bound}
M = \max \Bigl\{ n , \todo{Mark:log:bounds}{\bigl\lfloor 
\log_{\rho}(r_1/r_2)\bigr\rfloor}\Bigr\},
%\frac{\log(r_2/r_1)}{\log(1/\rho)}\right\rfloor} \right\},
\end{equation}
and it follows that $\mathcal{X}^\infty$ is a bounded polytopic set.
\end{proof}
%

@@

\begin{cor}
Let $c_1$, $c_2$ and $c_3$ denote respectively the radii of: %
the largest ball centered on the origin contained in $\mathcal{X}$, 
%
the smallest ball centered on the origin that contains $\mathcal{P}_n$, and
%
the smallest ball centered on the origin that contains $\mathcal{V}_1(x)$ for all $x\in\mathcal{X}$.
%
If $c_i > (1-\rho)^{-1}c_3$ for $i=1,2$, then $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:cbound}
M = \max \biggl\{ n , 
\todo{Mark:log:bounds}{
\biggl\lfloor \log_{\rho}\Bigl(\frac{c_1-(1-\rho)^{-1}c_3}{c_2-(1-\rho)^{-1}c_3}\Bigr)\biggr\rfloor \biggr\}}.
\end{equation}
\end{cor}
%

\begin{proof}
\todo{Mark:proof:cor15}{%
\def\X{\mathcal{X}}%
\def\D{\mathcal{D}}%
\def\V{\mathcal{V}}%
\def\E{\mathcal{E}}%
%
The iteration (\ref{eq:Xk:iteration}) can be defined  equivalently as $\X_0=\X$ and $\X_k = \X_{k-1} \cap \D_k^\prime$ for $k=1,2,\ldots$, with
\[
\D_k^\prime = \bigl\{ x\in\X_{k-1} : \{\Psi x\} \oplus \V(x) If \subseteq \D_{k-1}^\prime\}
\]
for $k=1,2,\ldots$ and $\D_0^\prime=\X$. Clearly $\X_k\subseteq \X$ for all $k$, and since $V_1(x)\subseteq c_3\E$ for all $x\in\X$ (where $\E = B_1(0)$), it follows that $\D^\prime_k \supseteq \Psi^{-1}(\D_{k-1}^\prime \ominus c_3\E)$ and 
\[
\D_k^\prime 
\supseteq 
%\Psi^{-k}\ominus \bigoplus_{i=0}^k c_3 \Psi^{-i}\E=
\Psi^{-k} \Bigl[ \X \ominus \bigoplus_{i=0}^{k-1} c_3\Psi^i\E \Bigr]
\supseteq 
\Bigl[ c_1 - \Bigl(\frac{1-\rho^k}{1-\rho} \Bigr) c_3\Bigr] \rho^{-k}\mathcal{E} 
\]
since $\X\subseteq c_1\E$. 
%
Therefore $\D_k^\prime\neq \emptyset$ for all $k$ if $c_1 > (1-\rho)^{-1}c_3$, and in this case, since $\X_{k-1} \subseteq \mathcal{P}_n\subseteq c_2\E$ for all $k\geq n+1$, we have $\X_{k-1}\subseteq \D_k^\prime$ if $c_2\rho^k \leq c_1 - c_3(1-\rho^k)/(1-\rho)$. 
%
Hence $\X^\infty=\X_M$, where $M$ is 
%given by (\ref{eq:iteration:cbound}).}
the smallest integer such that $k= M+1$ satisfies this condition, which is given by (\ref{eq:iteration:cbound})
since $c_2>(1-\rho)^{-1}c_3$ is assumed.}
%
% If $\mathcal{V}(x)\subseteq c_3\mathcal{E}$ for all $x\in\mathcal{X}$, then since $\mathcal{X}_k\subseteq\mathcal{X}$ for all $k$, we have $\mathcal{R}_k \supseteq \mathcal{R}_{k-1}\ominus \rho^{k-1} c_3\mathcal{E}$ from (\ref{eq:Rk:iteration}), and hence
% \[
% \mathcal{R}_k \supseteq \mathcal{X} \ominus \sum_{i=0}^{k-1} \rho^{i} c_3\mathcal{E} 
% %=\mathcal{X} \ominus \Bigl(\frac{1-\rho^k}{1-\rho} \Bigr) c_3 \mathcal{E}.
% \supseteq \Bigl[ c_1 - \Bigl(\frac{1-\rho^k}{1-\rho} \Bigr) c_3\Bigr] \mathcal{E}.
% \]
% where $c_1 \mathcal{E} \subseteq \mathcal{X}$. 
% %
% Therefore $\mathcal{R}^\infty \supseteq \bigl( c_1 - (1-\rho)^{-1}c_3\bigr) \mathcal{E} \neq \emptyset$ if $c_1\geq (1-\rho)^{-1}c_3$,
% %
% in which case $\mathcal{X}_k \subseteq \mathcal{P}_n \subseteq c_2 \mathcal{E}$ for all $k\geq n$ implies that $\mathcal X^\infty = \mathcal X_M$ where $M$ is given by (\ref{eq:iteration:cbound}).
\end{proof}
